Local simple connectedness of boundaries of hyperbolic groups

### 2020-06-22 paper.tex
minor changeds?

\begin{abstract}
  In this paper we prove a theorem describing the local topology of the
  boundary of a hyperbolic group in terms of its global topology: the boundary
  is locally simply connected if and only if the complement of any point in the
  boundary is simply connected. This generalises a theorem of Bestvina and
  Mess~\cite{bestvinamess91}.
\end{abstract}

@@

The goal of this paper is to prove the following theorem, which restricts the
local complexity of the boundary of a hyperbolic group in terms of its global
complexity in a similar way to the theorem of Bestvina and Mess described
above.

@@

The paper is structured as follows. In Section~\ref{sec:spheres} we use the
Rips complex of the group $G$ to build a sequence $(K_n)_{n \geq 0}$ of
simplicial complexes that give successively better approximations to the
boundary $\boundary G$. These simplicial complexes are spheres in the Rips
complex. There exist natural simplicial maps $p^n_m\from K_n\to K_m$ for $n \gg
m$, and there exist natural continuous maps $p^\infty_n\from\boundary G \to
K_n$ for all $n$.  The remainder of Section~\ref{sec:spheres} will be spent
proving quantitative statements about these maps.

@@

Finally, in Section~\ref{sec:conclusion} we put the results of the previous
sections together to prove Theorem~\ref{thm:main_theorem}, and conclude the
paper with some questions about strengthenings and generalisations.

@@

We begin this section by recalling work of Bestvina and Mess, Bowditch, and
Swarup, which characterise the hyperbolic groups with locally path connected
boundary. In~\cite{bestvinamess91}, Bestvina and Mess introduce the following
condition that a hyperbolic group might satisfy. (When comparing the constants
appearing in our definition of the condition with that in the cited paper, note
that with our convention that ideal triangles are $\delta$-hyperbolic, Bestvina
and Mess's constant $C$ can be taken to be equal to $\delta$.)

@@

It is also natural to ask whether the theorem of this paper generalises to
higher dimensions. The difficulty is in generalising the proof of
Proposition~\ref{prop:sufficient_condition}: given a sequence of maps from $S^0$
to $\boundary G$ we pass to a uniformly convergent subsequence, but this is not
possible for higher dimensional spheres without controlling the modulus of
continuity of the maps.

>>>>

\begin{abstract}
  In this article we prove a theorem describing the local topology of the
  boundary of a hyperbolic group in terms of its global topology: the boundary
  is locally simply connected if and only if the complement of any point in the
  boundary is simply connected. This generalises a theorem of Bestvina and
  Mess~\cite{bestvinamess91}.
\end{abstract}

@@

The goal of this article is to prove the following theorem, which restricts the
local complexity of the boundary of a hyperbolic group in terms of its global
complexity in a similar way to the theorem of Bestvina and Mess described
above.

@@

The article is structured as follows. In Section~\ref{sec:spheres} we use the
Rips complex of the group $G$ to build a sequence $(K_n)_{n \geq 0}$ of
simplicial complexes that give successively better approximations to the
boundary $\boundary G$. These simplicial complexes are spheres in the Rips
complex. There exist natural simplicial maps $p^n_m\from K_n\to K_m$ for $n \gg
m$, and there exist natural continuous maps $p^\infty_n\from\boundary G \to
K_n$ for all $n$.  The remainder of Section~\ref{sec:spheres} will be spent
proving quantitative statements about these maps.

@@

Finally, in Section~\ref{sec:conclusion} we put the results of the previous
sections together to prove Theorem~\ref{thm:main_theorem}, and conclude the
article with some questions about strengthenings and generalisations.

@@

We begin this section by recalling work of Bestvina and Mess, Bowditch, and
Swarup, which characterise the hyperbolic groups with locally path connected
boundary. In~\cite{bestvinamess91}, Bestvina and Mess introduce the following
condition that a hyperbolic group might satisfy. (When comparing the constants
appearing in our definition of the condition with that in the cited article, note
that with our convention that ideal triangles are $\delta$-hyperbolic, Bestvina
and Mess's constant $C$ can be taken to be equal to $\delta$.)

@@

It is also natural to ask whether the theorem of this article generalises to
higher dimensions. The difficulty is in generalising the proof of
Proposition~\ref{prop:sufficient_condition}: given a sequence of maps from $S^0$
to $\boundary G$ we pass to a uniformly convergent subsequence, but this is not
possible for higher dimensional spheres without controlling the modulus of
continuity of the maps.
